\documentclass{article}

\usepackage{geometry}
\usepackage{url}

\title{Biggest Problem In The City}  % Replace with your title
\author{Muhammad Furqan Karim} % Replace with your name

\begin{document}
\maketitle

\section{The Text}

\begin{quotation}
  ``The First word my nephew Nadir uttered as a child over 25 years ago was 'tanker'. Hardly surprising as the arrival of the vehicle carrying water to his home was a regular event.For the majority of houses in Karachi especially in DHA, buying tankers is the only means of getting water.So clearly, enough water is reaching the city; the question is why can’t the city and provincial authorities supply it to homes? The answer lies in the vast amounts collected by the owners of the numerous tankers that ferry water around the city and the broken old lines use to supply water. Apart from it the population has also been increasing exponentially so that the water isn't sufficient for the citizens.''
\end{quotation}


\section{Inferred Information}

\begin{itemize}
\item Karachi has become the hub of Water crises.
\item Karachi's Defence society is one of the country's most expensive localities.
\item For majority of houses in DHA even, buying tankers is the only means of getting water.
\item One of the major reason for this problem is that Karachi has grown exponentially.
\item Due to unexpected rise in population, the water crisis has increased.
\item The main pipelines through which water is divided into local areas have become old and are not fitful to supply water to the houses.
\end{itemize}

\section{The Argument}

There are two conclusions in this argument.

First conclusion:
\begin{itemize}
\item The local areas in Karachi do not have a proper water pipeline system.
\end{itemize}

Including the above conclusion as a premise, the further conclusion is:
\begin{itemize}
\item The water in the city is not sufficient for the whole population of Karachi.
\end{itemize}

According to the above argument, the only means of getting enough water for houses in most of the areas is to buy water tankers in Karachi. If all the premises are true, then the conclusion follows. I cannot find a counterexample. Therefore, the argument is valid.

\end{document}
